\documentclass[11pt]{article}

\usepackage[margin = 1in]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}

\usepackage{multirow}


\begin{document}
%\maketitle

\section*{Rubrics for Final Project}

\setlength{\parindent}{0pt}

The final project is graded based on the following deliverables:
\begin{itemize}
	\item Presentation of results and insight: 40\%
	\item Data analysis source code and data: 40\%
	\item Final project report: 20\%
\end{itemize}

Below is a breakdown of the 3 deliverables:

\subsection{Presentation of results and insights (40\%)}
\begin{itemize}
	\item Each team will have 10 minutes to present their findings and 2 minutes to answer questions.
	\item You must present your results in some form, such as Powerpoint slides, a Jupyter notebook, a pdf file, or a dashboard UI, etc.
	\item This is where you should address any problem you had in converting
	your initial design into a result. If you do not address and reflect on issues in your code, you will likely lose points in both this section and in source code part.
	\item Explain what your numerical results mean. If you are using statistical methods, try to explain why you use these methods and how you have used them to obtain meaningful results.
	\item Don’t forget to mention any reflections on how you might have been able to improve your process if you were to do it again.	
\end{itemize}	

\subsection{Data analysis source code and data (40\%)}
\begin{itemize}
	\item Your source code should be written in a Jupyter notebook file with all the source code and corresponding execution results.	
	\item If data size allows, the datasets you used for your data analysis should be packaged with the source code. If it is not feasible, please list the precise source/url on the dataset you used.
	\item The jupyter notebook file should contain all the source code that's relevant to the results you presented in the project presentation.
	\item Your code in the Jupyer notebook file should be executable. All the listed results in the notebook should be reproducible by executing the code cells one by one.
	\item Comment and document your work! Your code should be easy to understand and has enough comments/annotations to guide the reader through the data analysis. 
	\item As always, please don’t submit messy or redundant code. Name your files and variables meaningfully (avoid using variables named with a single letter).
	
\end{itemize}	

\subsection{Final project report (20\%)}
\begin{itemize}
	\item The report should contain some background information about data and the problem to solve
	\item The report should have a summary on the analytics methodologies used in the analysis and
	\item The report should have a summary on the data analysis results and findings
	\item The report should list each team member's contribution to the project
\end{itemize}




\end{document}